Storing messages with multipartite neural cliques

### 2014-07-02 Articles/article.tex
...

	\subsubsection{Simulations}
		gap of theoretical density with density in simulations : under $1$ percent
		Improves the retrieval rate for multiple iterations and/or corrupted messages.

@@

	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
	For one iteration, it is less efficient.
	\begin{figure}
		\includegraphics[width=8.5cm]{densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
	\end{figure}

	\begin{figure}
		\includegraphics[width=8.5cm]{remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\end{figure}

@@

	\subsection{Retrieving corrupted messages}
	\begin{figure}
		\includegraphics[width=8.5cm]{remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
	\end{figure}

		\begin{figure}
		\includegraphics[width=8.5cm]{remplacement_figure4g1}
		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
	\end{figure}

	Spéculations en Français :

@@

		a priori for noise on edges :
	\newpage
	l
	\newpage
	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$

	gc : good (à remplacer par right) neuron in correct cluster

	\begin{align*}
	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
	\end{align*}

	generalisation to multiple activities per cluster :

	%Marche mieux pouur de petits c --> le faire sur le sparse ?
	\nocite{*}
	\bibliographystyle{numeric} % Le style est mis entre crochets.
         \bibliography{bibli.bib}
\end{document}

>>>>

	\subsubsection{Simulations}
		gap of theoretical density with density in simulations : under $1$ percent

		New rule : Improves the retrieval rate for multiple iterations and/or corrupted messages.

@@

	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
	For one iteration, it is less efficient.
	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
	\end{figure}

	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\end{figure}

@@

	\subsection{Retrieving corrupted messages}
	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
	\end{figure}

		\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure4g1}
		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
	\end{figure}

	gc : good (à remplacer par right/wrong ?) neuron in correct cluster

	$
	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
	$

	generalisation to multiple activities per cluster :
	\newpage
	a
	\newpage

	%Marche mieux pouur de petits c --> le faire sur le sparse ?

	\section{Resilience}
	Spéculations en Français :

@@

		a priori for noise on edges :

	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$	
	\nocite{*}
	\bibliographystyle{numeric} % Le style est mis entre crochets.
         \bibliography{bibli.bib}
\end{document}
